Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-04-03 article/manuscript.Rnw
add DOI for Mendeley data
change forum to uppercase in title

\begin{frontmatter}
\title{Survival Analysis of Questions Posted on the iFixit Answers forum}

@@

All computation was executed under \texttt{R} version 3.4.3.  Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R. To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package. This function uses the Cox model and a vector of times to compute predictions. Data used for this analysis can be found here(Mendeley citation). Cited data includes all variables used in the model. Code for variable setup and analysis is available upon request.

>>>>

\begin{frontmatter}
\title{Survival Analysis of Questions Posted on the iFixit Answers Forum}

@@

All computation was executed under \texttt{R} version 3.4.3.  Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R. To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package. This function uses the Cox model and a vector of times to compute predictions. Data used for this analysis was published on Mendeley Data (DOI: 10.17632/shfkj785yb.1). Code for variable setup and analysis is available upon request.
